\documentclass{article}
\usepackage[margin=1in]{geometry}

\title{Design Document}
\author{Jacob Reckhard \and Navras Kamal \and Radomir Wasowski}

\begin{document}
\maketitle

Is it worth writing a small intro? Your design document must be type-written and is saved as a PDF and be included in your submission. Your design document cannot exceed 4 pages. The design document should include the following sections. The design document should also include a documentation of any decision you have made which is not in the project specification or any coding you have done beyond or different from what is required. Your design document will not include the source code. However your source code will be inspected for source code quality (whether the code is easy to read and if data processing is all done in SQL and not in the application) and self-documentation (whether the code is properly commented).

\section{User Guide}
a general overview of your system with a small user guide\\
The general overview of the system gives a high level introduction and may include a diagram showing the flow of data between different components; this can be useful for both users and developers of your application.

\section{Design}
a detailed design of your software with a focus on the components required to deliver the major functions of your application\\
The detailed design of your software should describe the responsibility and interface of each primary function or class (not secondary utility functions/classes) and the structure and relationships among them. Depending on the programming language being used, you may have methods, functions or classes.

\section{Testing Strategy}
your testing strategy\\
The testing strategy discusses your general strategy for testing, with the scenarios being tested, the coverage of your test cases and (if applicable) some statistics on the number of bugs found and the nature of those bugs.

\section{Group Management}
your group work break-down strategy\\
The group work strategy must list the break-down of the work items among partners, both the time spent (an estimate) and the progress made by each partner, and your method of coordination to keep the project on track.

\end{document}
