Your group work break-down strategy.

The group work strategy must list the break-down of the work items among partners, both the time spent (an estimate) and the progress made by each partner, and your method of coordination to keep the project on track.

The group was composed of 3 members, Navras Kamal, Jacob Reckhard, and Radomir Wasowski.  Each member was assigned certain tasks to implement, and all members worked together to test and incorportate these individual components into the final project.  Navras was responsible for Registering a Birth and Registering a Marriage.  Radomir was responsible for Process a Bill of Sale, Process a Payment, and Get a Driver Abstract.  Jacob was responsible for Renew a Vehicle Registration, Issue a Ticket, and Find a Car Owner.  These responsabilities were assigned unanimously by the group.  Everyone also worked together to create sample data, tests, and this report.  

An estimate for the hours spent and progress made by each member is broken down as follows
\begin{itemize}
\item{Jacob: 29 hours, completed all assigned work items, created secondary functions for ease of use}
\item{Navras: 23 hours, completed all assigned work items}
\item{Radomir: 25 hours, completed all assigned work items}
\end{itemize}

The team was coordinated through a combination of in person meetings and communication via Discord and email.  When the spec was released, the team worked together in person to split the responsabilities.  After that we would check in through in person meetings and online to confirm tasks were being completed.  To track progress we created a checklist and used GitHub to track and merge changes / updates from each contributor.  Each individual was tasked with managing their own time to complete their assigned tasks, using whatever methods they found effective (ie. checklists, notes, reminders...).  Overall this communication was effective in keeping progress on track.  
